Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-09-19 draft_lm1.tex
minor changes to d manuscript

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Estimating the Initial Susceptible Fraction in Dengue Dynamics}
}
% Insert Author names, affiliations and corresponding author email.
\\
Flavio Code\c{c}o Coelho$^{1}$, 
Luiz Max de Carvalho$^{2}$, 
Author3$^{3,\ast}$
\\
\bf{1} School of Applied Mathematics, Get\'ulio Vargas Foundation (FGV), Rio de Janeiro -- RJ, Brazil.
\\
\bf{2} Program for Scientific Computing (PROCC), Oswaldo Cruz Foundation, Rio de Janeiro -- RJ, Brazil.
\\
$\ast$ E-mail: fccoelho@fgv.br
\end{flushleft}

% Please keep the abstract between 250 and 300 words
\section*{Abstract}

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}

\section*{Introduction}
% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Methods}
\subsection*{The model}
\subsection*{Parameter estimation using Bayesian melding}
% Results and Discussion can be combined.
\section*{Results}

% We only support three levels of headings, please do not create a heading level below \subsubsection.
\subsection*{Subsection 1}

\section*{Discussion}

% Do NOT remove this, even if you are not including acknowledgments.

\section*{Acknowledgments}
LMC is grateful to Dr. Leonardo Bastos for useful discussions.

\section*{References}
\bibliography{lm1}
\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Estimating the Initial Susceptible Fraction in Dengue Dynamics}
}
% Insert Author names, affiliations and corresponding author email.
\\
Flavio Code\c{c}o Coelho$^{1\ast}$, 
Luiz Max de Carvalho$^{2}$, 
\\
\bf{1} Escola de Matem\'atica Aplicada , Funda\c{c}\~ao Get\'ulio Varga (FGV), Rio de Janeiro -- RJ, Brazil.
\\
\bf{2} Programa de Computa\c{c}\~ao Cient\'ifica (PROCC), Funda\c{c}\~ao Oswaldo Cruz, Rio de Janeiro -- RJ, Brazil.
\\
$\ast$ E-mail: fccoelho@fgv.br
\end{flushleft}

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
Our paper is just awesome.
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}

\section*{Introduction}
% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Methods}
\subsection*{The model}
\subsection*{Parameter estimation using Bayesian melding}
% Results and Discussion can be combined.
\section*{Results}
% We only support three levels of headings, please do not create a heading level below \subsubsection.
%\subsection*{Subsection 1}
\section*{Discussion}
% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
LMC is grateful to Dr. Leonardo Bastos for useful discussions on the estimation of $R(t)$.
\section*{References}
\bibliography{lm1}
\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}
